---
title: "Instagram Influencer Marketing Research"
author: "Mansukh Kaur"
date: "14/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(knitr)
hashtag=read.csv("hashtagdata.csv")
attach(hashtag)
library(reshape2)
```

```{r echo=FALSE}


```
## Dataset

### Instagram Post Data
**(based on hastags)**  

```{r}

kable(head(hashtag,1),caption = "Number of Posts for each Hashtag ", floating.environment="sidewaystable",align = "lccrr")
```



### Since we see quite irrevalent data such as URLs, Location IDs,PostIDs, etc. Cleaning the data by removing the unncessary columns  

```{r }
hashtag=subset(hashtag,select= names(hashtag)[!names(hashtag) %in%c("postUrl", "profileUrl", "fullName","instagramPostUrl","timestamp","postId","videoUrl","locationId","imgUrl","X") ])

l=kable(head(hashtag),caption = "Data Frame relevant to the Project", floating.environment="sidewaystable",align = "lccrr") 
l
#view
```
# Cleaning Data
## 1. Changing format of pubDate to display only date
## 2. Removing NA values

```{r}
hashtag$pubDate=as.Date(hashtag$pubDate)
hashtag$isSidecar[is.na(hashtag$isSidecar)]=FALSE
hashtag$viewCount[is.na(hashtag$viewCount)]=0
hashtag$commentCount[is.na(hashtag$commentCount)]=0
hashtag$likeCount[is.na(hashtag$likeCount)]=0
hashtag$type[is.na(hashtag$type)]="Video"



```
## The data is now *tidy*.
```{r echo=FALSE}

kable(head(hashtag),caption = "Cleaned Data Frame ", floating.environment="sidewaystable",align = "lccrr")

```

```{r echo=FALSE}
h1=(unique(hashtag$query))
kable(h1,caption = "Posts for the following Hashtags were scraped", floating.environment="sidewaystable",align = "lccrr")
```


```{r}
dis=hashtag%>%group_by(type)%>%count(type)
ggplot(dis,aes(x="",y=n,fill=type))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y",start=0)+labs(title = "Post Distribution",x=" ",y=" ")+
  geom_text(aes(label = n),
            position = position_stack(vjust = 0.5))

```

## Number of Posts per Hashtag is given by


```{r echo=FALSE}
posts=hashtag%>%group_by(query)%>%count(query)
No_of_Posts=posts$n
Hashtag<-posts$query
ggplot(data=posts, aes(x=Hashtag, y=No_of_Posts , fill=No_of_Posts ))+
  geom_bar(stat="identity",color="purple")+
  theme(axis.text.x = element_text(angle=90))+labs(title = "Number of Posts per Hashtag", x="HASHTAGS", y="Number of Posts",caption = "  ")  

#------------------------------

  
```



## Number of *Photos and Videos* each per Hashtag
```{r}
ss=hashtag[,c("query","type")]
s1=ss%>%group_by(query,type)%>%count(type)
#View(s1)

ggplot(s1, aes(x=query, y=n, fill=type)) +
    geom_bar(stat='identity')+theme(axis.text.x = element_text(angle=90))+labs(x="Hashtags",y="Number of Posts")
#--------
```

## Analysing how well Photos and Videos performed for each Hashtag  
### Let's consider Photos first
```{r echo=FALSE}
ss=hashtag[,c("query","likeCount","commentCount","viewCount","type")]
s1=ss%>%group_by(query,type)%>%summarise(Likes=mean(likeCount),Comments=sum(commentCount),mean(viewCount))
#View(sss)
s2=subset(s1, type == "Photo")
s2=s2[ , c(1,3,4)]
sss=melt(s2,id.vars = "query")
#head(sss)
ggplot(sss, aes(x=query, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge')+theme(axis.text.x = element_text(angle=90))+
    labs(x="Hashtags",y="Count")
#View(sss)
```


We can see that engagement is mostly in the form of Likes for most of the Hashtags



### Let's see how Videos perform 
```{r}
ss=hashtag[,c("query","likeCount","commentCount","viewCount","type")]
s1=ss%>%group_by(query,type)%>%summarise(Likes=mean(likeCount),Comments=sum(commentCount),Views=mean(viewCount))
#View(sss)
s2=subset(s1, type == "Video")
s2=s2[ , c(1,3,4,5)]
sss=melt(s2,id.vars = "query")
#head(sss)
ggplot(sss, aes(x=query, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge')+theme(axis.text.x = element_text(angle=90))+labs(x="Hashtag",y="Count")
```


We can see Views have huge impact on engagement.



### Generally, let's check, How Photos and Videos Generate Engagement
```{r echo=FALSE}
typeLikes=hashtag%>%group_by(type)%>%summarise(mean(likeCount),mean(commentCount),mean(viewCount)) 
typeWiseCount=hashtag%>%group_by(type)%>%count(type)


#View(typeLikes)
df2 <- data.frame(t(typeLikes[-1]))
df2=cbind(df2,c("Likes","Comments","Views"))
colnames(df2) <- c("Photo","Video","Engagement_Type")

p=data.frame(df2[,c(1,3)])
ggplot(p,aes(x="",y=Photo,fill=Engagement_Type))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y",start=0)+labs(title = "Engagement from Photos", x=" ", y=" ")

chkMulPhotos=hashtag%>%group_by(type,isSidecar)%>%count(isSidecar)%>%summarise(sum(likeCount))

chkMulPhotos1=hashtag%>%group_by(type,isSidecar)%>%summarise(mean(likeCount))
View(df2)
q=data.frame(df2[,c(2,3)])
ggplot(q,aes(x="",y=Video,fill=Engagement_Type))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y",start=0)+labs(title = "Engagement from Videos",x=" ",y=" ")



```


### We can see that extra Views attribute of Videos brings a drastic change in total engagement
```{r}
ss=hashtag[,c("query","likeCount","commentCount","viewCount","type","pubDate")]
s1=ss%>%group_by(query,type)%>%summarise(Likes=mean(likeCount), Comments=sum(commentCount), Views=mean(viewCount), total=Likes+Comments+Views)
s3=ss%>%group_by(query)%>%summarise(x=min(as.Date(pubDate)), y=max(as.Date(pubDate)), days=y-x)
s2=subset(s1, type == "Video")
s2=s2[ , c(1,3,4,5)]
sss=melt(s2,id.vars = "query")
#View(sss)
#head(sss)
ggplot(sss, aes(x=query, y=value, fill=variable)) +
    geom_bar(stat='identity', position='dodge')+
    theme(axis.text.x = element_text(angle=90))+
    labs(title = "Likes, Comments, Views Distribution per Hashtag",x="Hashtags",y="Count")
```


# Timeline of Posts for all the Hashtags VS total engagement

```{r}
ss=hashtag[,c("query","likeCount","commentCount","viewCount","type","pubDate")]
s1=ss%>%group_by(query,pubDate)%>%summarise(a=mean(likeCount), b=sum(commentCount), c=mean(viewCount), total=a+b+c)
s2=ss%>%group_by(query)%>%summarise(a=mean(likeCount), b=sum(commentCount), c=mean(viewCount), total=a+b+c)
s3=ss%>%group_by(query)%>%summarise(x=min(as.Date(pubDate)), y=max(as.Date(pubDate)), days=y-x)
ggplot(s1, aes(x=pubDate, y=total)) + 
  geom_area(col="deeppink" , fill="deeppink")+theme(axis.text.x = element_text(angle = 90))+facet_wrap(~ query,scales = "free")+labs(x="Timeline",y="Engagement")
```



## Total Engagement VS Nuumber of Days Plot


```{r}



x=s2$total
y=s3$days
z=s3$query
s5=cbind.data.frame(engagement=s2$total,days=s3$days,query=s3$query)
#s5=cbind(x,y,z)
s5=as.data.frame(s5)
#View(s5)
sd=melt(s5,id.vars = "query")






ggplot(data = s5, aes(x = query, y = engagement)) + 
  geom_bar(stat = "identity",col="deeppink",fill="deeppink") + 
  geom_line(data = s5, aes(x = query, y = days*100, group = 1,col="steelblue",name="Days"), inherit.aes = FALSE) +
  scale_y_continuous(sec.axis = sec_axis(~./100, name = "No of Days"))+
  theme(axis.text.x = element_text(angle=90),legend.position="none")+labs(x="Hashtags",y="Engagement")

cor(s2$total,as.numeric(s3$days))




```